\textsf{Are large language models superhuman chemists?}

### 2024-08-19 src/tex/ms.tex
Update src/tex/ms.tex

\subparagraph{Instruction-tuned models} In addition, we used Claude 2, Claude3 (Opus),\autocite{anthropicClaudeModelFamily2024} GPT-4,\autocite{openai2024gpt4} GPT-3.5-turbo,\autocite{brown2020language} Gemini Pro,\autocite{gemini} Mixtral-8x7b,\autocite{jiang2024mixtral} LLaMA2 (7B, 13B, 70B),\autocite{touvron2023llama} as well as the 7B chat model from Perplexity.AI.

>>>>

\subparagraph{Instruction-tuned models} In addition, we tested Claude 2, Claude3 (Opus),\autocite{anthropicClaudeModelFamily2024} GPT-4,\autocite{openai2024gpt4} GPT-3.5-turbo,\autocite{brown2020language} Gemini Pro,\autocite{gemini} Mixtral-8x7b,\autocite{jiang2024mixtral} LLaMA2 (7B, 13B, 70B),\autocite{touvron2023llama} and LLaMa3 (8B, 70B, 405B).
